Quantum Interval-Valued Probability: Contextuality and the Born Rule

### 2018-03-26 revised_prop_letter_ajhs.tex
revised_prop_letter_ajhs.tex Fix typos...

\newcommand{\imposs}{\textbf{\textsf{F}}}
\newcommand{\necess}{\textbf{\textsf{T}}}
\newcommand{\unknown}{\textbf{\textsf{U}}}

@@

We also investigate the second key aspect of imprecise quantum
measurement, which is its statistical nature as reflected in the
application of the Born rule determining the probability of a given
measurement outcome~\cite{Born1983bibTeX,Mermin2007,Jaeger2007}.
Here, Gleason's theorem establishes that there is no alternative to
the Born rule by demonstrating, using reasonable continuity arguments
in Hilbert spaces of dimension $d\ge3$, the existence of a unique
state $\rho$ consistent with the statistical predictions computed from
the Born rule~\cite{gleason1957,Redhead1987-REDINA,peres1995quantum}.
Our question then concerns what happens when infinite precision cannot
be achieved.  We are able to show that, while a QIVPM incorporating
the effects of finite precision might not be consistent with Gleason's
unique state~$\rho$ on all projectors defined on a Hilbert
space~$\Hilb$ of dimension $d\ge3$, there is a mathematically precise
sense in which one recovers the original Gleason theorem
asymptotically.  Specifically, it is possible to construct a class of
QIVPMs representing bounded resources that is parameterized by the
size of the intervals. We then demonstrate that all QIVPMs in this
class are consistent with a non-empty ``ball'' of quantum states whose
radius is defined by the maximal length of the intervals
characterizing the uncertainties. As the size of the intervals goes to
zero, this ball of quantum states converges to a point representing
the unique state consistent with the Born rule and Gleason's theorem.

>>>>

\newcommand{\interval}[1]{{\normalfont\textsf{\textbf{#1}}}}
\newcommand{\imposs}{\interval{F}}
\newcommand{\necess}{\interval{T}}
\newcommand{\unknown}{\interval{U}}

@@

We also investigate the second key aspect of imprecise quantum
measurement, which is its statistical nature as reflected in the
application of the Born rule \cite{Born1983bibTeX,Mermin2007,Jaeger2007} determining the probability of a given
measurement outcome.
Here, Gleason's theorem \cite{gleason1957,Redhead1987-REDINA,peres1995quantum} establishes that there is no alternative to
the Born rule by demonstrating, using reasonable continuity arguments
in Hilbert spaces of dimension $d\ge3$, the existence of a unique
state $\rho$ consistent with the statistical predictions computed from
the Born rule.
Our question then concerns what happens when infinite precision cannot
be achieved.  We are able to show that, while a QIVPM incorporating
the effects of finite precision might not be consistent with Gleason's
unique state~$\rho$ on all projectors defined on a Hilbert
space~$\Hilb$ of dimension $d\ge3$, there is a mathematically precise
sense in which one recovers the original Gleason theorem
asymptotically.  Specifically, it is possible to construct a class of
QIVPMs representing bounded resources that is parameterized by the
size of the intervals. We then demonstrate that all QIVPMs in this
class are consistent with a non-empty ``ball'' of quantum states whose
radius is defined by the maximal length of the intervals
characterizing the uncertainties. As the size of the intervals goes to
zero, this ball of quantum states converges to a point representing
the unique state consistent with the Born rule and Gleason's theorem.
